A Roadmap for\\HEP Software and Computing R\&D\\for the 2020s

### 2018-04-16 CWP/papers/HSF-CWP-2017-01_roadmap/latex/authors.tex
CWP + DOMA paper: update author list with fixed a2tex

Albrecht, Johannes$^{66}$;
Alves Jr, Antonio Augusto$^{79}$;

@@

Anh-Ky, Nguyen$^{117}$;
Aphecetche, Laurent$^{63}$;

@@

Asai, Makoto$^{61,p}$;

@@

@@

Benjamin, Douglas$^{80}$;
Bernius, Catrin$^{61}$;
Bhimji, Wahid$^{44}$;
Bianchi, Riccardo Maria$^{102}$;

@@

Biscarat, Catherine$^{50}$;

@@

Bloom, Kenneth$^{94}$;

@@

Bockelman, Brian$^{94}$;
Bold, Tomasz$^{41}$;

@@

Boveia, Antonio$^{98}$;

@@

Bracko, Marko$^{91,39}$;
Britton, David$^{84}$;
Buckley, Andy$^{84}$;

@@

Calafiura, Paolo$^{44}$;

@@

Castro, Nuno$^{45,93,d}$;

@@

Chang, Philip$^{73}$;
Chapman, John$^{74}$;

@@

Clarke, Peter$^{81}$;

@@

Cogneras, Eric$^{48}$;
Collier, Ian$^{59}$;

@@

Costanzo, Davide$^{108}$;

@@

Cranmer, Kyle$^{55}$;

@@

Crooks, David$^{84}$;
Crépé-Renaudin, Sabine$^{50}$;

@@

De, Kaushik$^{110}$;
De Cian, Michel$^{85}$;

@@

@@

Doglioni, Caterina$^{89,h}$;
Dotti, Andrea$^{61,p}$;

@@

Duflot, Laurent$^{43}$;

@@

Egede, Ulrik$^{36}$;
Elmer, Peter$^{103,a}$;

@@

Ferber, Torben$^{71}$;
Filipcic, Andrej$^{39}$;
Fisk, Ian$^{62}$;

@@

Flix, José$^{57,7,g}$;
Formica, Andrea$^{37}$;
Forti, Alessandra$^{90}$;
Frost, James$^{101}$;

@@

Gardner, Robert$^{78}$;
Garonne, Vincent$^{99}$;

@@

George, Simon$^{60}$;
Geurts, Frank$^{104}$;

@@

Giagu, Stefano$^{106,33}$;
Giffels, Manuel$^{40}$;
Gingrich, Douglas$^{67}$;

@@

Gligorov, Vladimir V.$^{49}$;
Glushkov, Ivan$^{110}$;
Gohn, Wesley$^{86}$;

@@

González Caballero, Isidro$^{100}$;
González Fernández, Juan R.$^{100}$;

@@

Grasland, Hadrien$^{43}$;
Gray, Heather$^{44}$;
Grillo, Lucia$^{90}$;
Guan, Wen$^{115}$;

@@

Gyurjyan, Vardan$^{38}$;
Hanushevsky, Andrew$^{61,p}$;

@@

Hauth, Thomas$^{40}$;

@@

Heinrich, Lukas$^{55}$;

@@

Hildreth, Michael$^{96,f}$;
Hodgkinson, Mark$^{108}$;
Hoeche, Stefan$^{61,p}$;

@@

Huang, Xingtao$^{107}$;
Ivanchenko, Vladimir N.$^{5,111}$;
Ivanov, Todor$^{109}$;
Jashal, Brij$^{65}$;

@@

Jones, Roger$^{87,a}$;
Jouvin, Michel$^{43,a}$;

@@

Kagan, Michael$^{61,p}$;
Kalderon, Charles William$^{89}$;

@@

Katz, Daniel S.$^{77}$;

@@

Kersevan, Borut Paul$^{88}$;

@@

Klute, Markus$^{51}$;

@@

Konstantinov, Dmitri$^{58}$;
Koppenburg, Patrick$^{54}$;

@@

Kreczko, Luke$^{70}$;
Kuhr, Thomas$^{47,a}$;

@@

Lampl, Walter$^{69}$;

@@

Lange, David$^{103,a}$;

@@

Leggett, Charles$^{44}$;
Letts, James$^{73}$;

@@

Li, Teng$^{81}$;
Lima, Guilherme$^{16}$;
Linacre, Jacob$^{59,m}$;

@@

@@

Love, Peter$^{87}$;

@@

Marshall, Zachary L$^{44}$;

@@

Martin-Haugh, Stewart$^{59}$;

@@

Mazumdar, Kajari$^{65}$;
McCauley, Thomas$^{96}$;

@@

McKee, Shawn$^{92,l}$;
McNab, Andrew$^{90}$;
Mehdiyev, Rashid$^{76}$;

@@

Mete, Alaettin Serhan$^{72}$;

@@

Mitrevski, Jovan$^{47}$;

@@

Morgan, Ben$^{114}$;
Mount, Richard$^{61,p}$;
Moyse, Edward$^{68}$;
Murray, Sean$^{75,10}$;
Neubauer, Mark S$^{77,a,k}$;
Novaes, Sérgio$^{105}$;

@@

Ozturk, Nurcan$^{110}$;
Pacheco Pages, Andres$^{57,20,j}$;
Paganini, Michela$^{116}$;
Pansanel, Jerome$^{35}$;
Pascuzzi, Vincent R.$^{112}$;
Patrick, Glenn$^{59}$;

@@

Pearson, Ben$^{52}$;

@@

Perdue, Gabriel$^{16}$;
Perez-Calero Yzquierdo, Antonio$^{57,7,g}$;

@@

Petersen, Troels$^{53}$;

@@

@@

Piilonen, Leo$^{118,i}$;

@@

@@

Polci, Francesco$^{49}$;

@@

Raven, Gerhard$^{54}$;

@@

Ritter, Martin$^{47}$;

@@

Rodrigues, Eduardo$^{79,a,e}$;

@@

Rousseau, David$^{43}$;
Roy, Gareth$^{84}$;

@@

Sakuma, Tai$^{70}$;

@@

Sartirana, Andrea$^{46}$;
Schellman, Heidi$^{56}$;

@@

Schramm, Steven$^{83}$;

@@

Seidel, Sally$^{95}$;
Sekmen, Sezen$^{42}$;
Serfon, Cedric$^{99}$;
Severini, Horst$^{97}$;

@@

Seymour, Michael$^{90}$;
Shapoval, Illya$^{44}$;

@@

Shiu, Jing-Ge$^{64}$;

@@

Skipsey, Sam$^{84}$;

@@

Sokoloff, Michael D$^{79,a}$;

@@

Stark, Giordon$^{6}$;
Stewart, Gordon$^{84}$;

@@

Sánchez, Arturo$^{113,19}$;

@@

Taffard, Anyes$^{72}$;
Templon, Jeff$^{54}$;

@@

Tsulaia, Vakhtang$^{44}$;
Tunnell, Christopher$^{6}$;

@@

Vallecorsa, Sofia$^{82}$;

@@

Vuosalo, Carl$^{115}$;
Vázquez Sierra, Carlos$^{54}$;

@@

@@

Winklmeier, Frank$^{56}$;

@@

Wuerthwein, Frank$^{73}$;
Wynne, Benjamin$^{81}$;

@@

Yang, Wei$^{61,p}$;

@@

\par {\footnotesize $^{6}$ Enrico Fermi Institute, University of Chicago, Chicago IL, USA}

@@

\par {\footnotesize $^{11}$ California Institute of Technology, Pasadena, California, USA}
\par {\footnotesize $^{12}$ Cornell University, Ithaca, USA}

@@

\par {\footnotesize $^{15}$ ETH Zurich - Institute for Particle Physics and Astrophysics (IPA), Zurich, Switzerland}
\par {\footnotesize $^{16}$ Fermi National Accelerator Laboratory, Batavia, USA}

@@

\par {\footnotesize $^{24}$ Department of Physics, Indiana University, Bloomington IN, USA}

@@

\par {\footnotesize $^{35}$ Université de Strasbourg, CNRS, IPHC UMR 7178, F-67000 Strasbourg, France}
\par {\footnotesize $^{36}$ Imperial College London, London, United Kingdom}
\par {\footnotesize $^{37}$ DSM/IRFU (Institut de Recherches sur les Lois Fondamentales de l’Univers), CEA Saclay (Commissariat à l’Énergie Atomique), Gif-sur-Yvette, France}
\par {\footnotesize $^{38}$ Thomas Jefferson National Accelerator Facility, Newport News, Virginia, USA}
\par {\footnotesize $^{39}$ Jožef Stefan Institute, Ljubljana, Slovenia}
\par {\footnotesize $^{40}$ Karlsruhe Institute of Technology, Karlsruhe, Germany}
\par {\footnotesize $^{41}$ AGH University of Science and Technology, Faculty of Physics and Applied Computer Science, Krakow, Poland}
\par {\footnotesize $^{42}$ Kyungpook National University, Daegu, Republic of Korea}
\par {\footnotesize $^{43}$ LAL, Université Paris-Sud and CNRS/IN2P3, Orsay, France}
\par {\footnotesize $^{44}$ Lawrence Berkeley National Laboratory and University of California, Berkeley CA, USA}
\par {\footnotesize $^{45}$ Laboratório de Instrumentação e Física Experimental de Partículas (LIP), Lisboa, Portugal}
\par {\footnotesize $^{46}$ Laboratoire Leprince-Ringuet, École Polytechnique, CNRS/IN2P3, Université Paris-Saclay, Palaiseau, France}
\par {\footnotesize $^{47}$ Fakultät für Physik, Ludwig-Maximilians-Universität München, München, Germany}
\par {\footnotesize $^{48}$ Laboratoire de Physique Corpusculaire, Clermont Université and Université Blaise Pascal and CNRS/IN2P3, Clermont-Ferrand, France}
\par {\footnotesize $^{49}$ LPNHE, Université Pierre et Marie Curie, Université Paris Diderot, CNRS/IN2P3, Paris, France}
\par {\footnotesize $^{50}$ Laboratoire de Physique Subatomique et de Cosmologie, Université Joseph Fourier and CNRS/IN2P3 and Institut National Polytechnique de Grenoble, Grenoble, France}
\par {\footnotesize $^{51}$ Department of Physics, University of Massachusetts, Amherst, MA, USA}
\par {\footnotesize $^{52}$ Max-Planck-Institut für Physik (Werner-Heisenberg-Institut), München, Germany}
\par {\footnotesize $^{53}$ Niels Bohr Institute, University of Copenhagen, Kobenhavn, Denmark}
\par {\footnotesize $^{54}$ Nikhef National Institute for Subatomic Physics and University of Amsterdam, Amsterdam, Netherlands}
\par {\footnotesize $^{55}$ Department of Physics, New York University, New York, NY, USA}
\par {\footnotesize $^{56}$ Center for High Energy Physics, University of Oregon, Eugene OR, USA}
\par {\footnotesize $^{57}$ Port d’Informació Científica (PIC), Universitat Autònoma de Barcelona (UAB), Barcelona, Spain}
\par {\footnotesize $^{58}$ High Energy Physics (IHEP), Protvino, Russia}
\par {\footnotesize $^{59}$ STFC Rutherford Appleton Laboratory, Didcot, United Kingdom}
\par {\footnotesize $^{60}$ Department of Physics, Royal Holloway University of London, Surrey, United Kingdom}
\par {\footnotesize $^{61}$ SLAC National Accelerator Laboratory, Menlo Park CA, USA}
\par {\footnotesize $^{62}$ Simons Foundation, New York, USA}
\par {\footnotesize $^{63}$ SUBATECH, IMT Atlantique, Université de Nantes, CNRS-IN2P3, Nantes, France}
\par {\footnotesize $^{64}$ National Taiwan University, Taipei, Taiwan}
\par {\footnotesize $^{65}$ Tata Institute of Fundamental Research, Mumbai, India}
\par {\footnotesize $^{66}$ Technische Universit\"at Dortmund, Dortmund, Germany}
\par {\footnotesize $^{67}$ Department of Physics, University of Alberta, Edmonton, AB, Canada}
\par {\footnotesize $^{68}$ Department of Physics, University of Massachusetts, Amherst, MA, USA}
\par {\footnotesize $^{69}$ Department of Physics, University of Arizona, Tucson, AZ, USA}
\par {\footnotesize $^{70}$ H.H. Wills Physics Laboratory, University of Bristol, Bristol, United Kingdom}
\par {\footnotesize $^{71}$ Department of Physics, University of British Columbia, Vancouver, BC, Canada}
\par {\footnotesize $^{72}$ Department of Physics and Astronomy, University of California Irvine, Irvine, CA, USA}
\par {\footnotesize $^{73}$ University of California, San Diego, La Jolla, USA}
\par {\footnotesize $^{74}$ Cavendish Laboratory, University of Cambridge, Cambridge, United Kingdom}
\par {\footnotesize $^{75}$ Physics Department, University of Cape Town, Cape Town, South Africa}
\par {\footnotesize $^{76}$ Carleton University, Ottawa, ON, Canada}
\par {\footnotesize $^{77}$ University of Illinois Urbana-Champaign, Champaign, Illinois, USA}
\par {\footnotesize $^{78}$ Enrico Fermi Institute, University of Chicago, Chicago, IL, USA}
\par {\footnotesize $^{79}$ University of Cincinnati, Cincinnati, OH, USA}
\par {\footnotesize $^{80}$ Department of Physics, Duke University, Durham, NC, USA}
\par {\footnotesize $^{81}$ SUPA - School of Physics and Astronomy, University of Edinburgh, Edinburgh, United Kingdom}
\par {\footnotesize $^{82}$ Gangneung-Wonju National University, South Korea}
\par {\footnotesize $^{83}$ Section de Physique, Université de Genève, Geneva, Switzerland}
\par {\footnotesize $^{84}$ SUPA - School of Physics and Astronomy, University of Glasgow, Glasgow, United Kingdom}
\par {\footnotesize $^{85}$ Physikalisches Institut, Ruprecht-Karls-Universitat Heidelberg, Heidelberg, Germany}
\par {\footnotesize $^{86}$ Department of Physics and Astronomy, University of Kentucky, Lexington, USA}
\par {\footnotesize $^{87}$ Physics Department, Lancaster University, Lancaster, United Kingdom}
\par {\footnotesize $^{88}$ Department of Physics, Jožef Stefan Institute and University of Ljubljana, Ljubljana, Slovenia}
\par {\footnotesize $^{89}$ Fysiska institutionen, Lunds Universitet, Lund, Sweden}
\par {\footnotesize $^{90}$ School of Physics and Astronomy, University of Manchester, Manchester, United Kingdom}
\par {\footnotesize $^{91}$ University of Maribor, Ljubljana, Slovenia}
\par {\footnotesize $^{92}$ Department of Physics, The University of Michigan, Ann Arbor, MI, USA}
\par {\footnotesize $^{93}$ Departamento de Física, Universidade do Minho, Braga, Portugal}
\par {\footnotesize $^{94}$ University of Nebraska-Lincoln, Lincoln, USA}
\par {\footnotesize $^{95}$ Department of Physics and Astronomy, University of New Mexico, Albuquerque NM, USA}
\par {\footnotesize $^{96}$ University of Notre Dame, Notre Dame, USA}
\par {\footnotesize $^{97}$ Homer L. Dodge Department of Physics and Astronomy, University of Oklahoma, Norman OK, USA}
\par {\footnotesize $^{98}$ The Ohio State University, Columbus, USA}
\par {\footnotesize $^{99}$ Department of Physics, University of Oslo, Oslo, Norway}
\par {\footnotesize $^{100}$ Universidad de Oviedo, Oviedo, Spain}
\par {\footnotesize $^{101}$ Department of Physics, Oxford University, Oxford, UK}
\par {\footnotesize $^{102}$ Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, PA, USA}
\par {\footnotesize $^{103}$ Princeton University, Princeton, USA}
\par {\footnotesize $^{104}$ Rice University, Houston, TX, USA}
\par {\footnotesize $^{105}$ Universidade Estadual Paulista, São Paulo, Brazil}
\par {\footnotesize $^{106}$ Dipartimento di Fisica, Università La Sapienza, Roma, Italy}
\par {\footnotesize $^{107}$ School of Physics, Shandong University, Shandong, China}
\par {\footnotesize $^{108}$ Department of Physics and Astronomy, University of Sheffield, Sheffield, United Kingdom}
\par {\footnotesize $^{109}$ University of Sofia, Sofia, Bulgaria}
\par {\footnotesize $^{110}$ Department of Physics, The University of Texas at Arlington, Arlington, TX, USA}
\par {\footnotesize $^{111}$ National Research Tomsk Polytechnic University, Tomsk, Russia}
\par {\footnotesize $^{112}$ Department of Physics, University of Toronto, Toronto, ON, Canada}
\par {\footnotesize $^{113}$ Dipartimento di Chimica, Fisica e Ambiente, Università di Udine, Udine, Italy}
\par {\footnotesize $^{114}$ Department of Physics, University of Warwick, Coventry, United Kingdom}
\par {\footnotesize $^{115}$ University of Wisconsin - Madison, Madison, WI, USA}
\par {\footnotesize $^{116}$ Department of Physics, Yale University, New Haven, CT, USA}
\par {\footnotesize $^{117}$ IOP and GUST, Vietnam Academy of Science and Technology (VAST), Hanoi, Vietnam}
\par {\footnotesize $^{118}$ Virginia Tech, Blacksburg, Virginia, USA}

>>>>

Albrecht, Johannes$^{68}$;
Alves Jr, Antonio Augusto$^{80}$;

@@

Anh-Ky, Nguyen$^{121}$;
Aphecetche, Laurent$^{65}$;

@@

Asai, Makoto$^{62,p}$;

@@

Banerjee, Sunanda$^{16,c}$;

@@

Benjamin, Douglas$^{81}$;
Bernius, Catrin$^{62}$;
Bhimji, Wahid$^{45}$;
Bianchi, Riccardo Maria$^{104}$;

@@

Biscarat, Catherine$^{51}$;

@@

Bloom, Kenneth$^{96}$;

@@

Bockelman, Brian$^{96}$;
Bold, Tomasz$^{42}$;

@@

Boveia, Antonio$^{100}$;

@@

Bracko, Marko$^{92,40}$;
Britton, David$^{85}$;
Buckley, Andy$^{85}$;

@@

Calafiura, Paolo$^{45}$;

@@

Castro, Nuno$^{46,95,d}$;

@@

Cervantes Villanueva, Javier$^{5}$;
Chang, Philip$^{74}$;
Chapman, John$^{75}$;

@@

Clarke, Peter$^{82}$;

@@

Cogneras, Eric$^{49}$;
Coles, Jeremy$^{75}$;
Collier, Ian$^{60}$;

@@

Costanzo, Davide$^{111}$;

@@

Cranmer, Kyle$^{56}$;

@@

Crooks, David$^{85}$;
Crépé-Renaudin, Sabine$^{51}$;
Currie, Robert$^{82}$;

@@

De, Kaushik$^{113}$;
De Cian, Michel$^{86}$;
De Roeck, Albert$^{5}$;
Delgado Peris, Antonio$^{7,g}$;
Derue, Frédéric$^{50}$;

@@

Di Guida, Salvatore$^{29}$;

@@

Doglioni, Caterina$^{90,h}$;
Dotti, Andrea$^{62,p}$;

@@

Duflot, Laurent$^{44}$;

@@

Egede, Ulrik$^{37}$;
Elmer, Peter$^{105,a}$;

@@

Farrell, Steven$^{45}$;
Ferber, Torben$^{72}$;
Filipcic, Andrej$^{40}$;
Fisk, Ian$^{63}$;

@@

Flix, José$^{58,7,g}$;
Formica, Andrea$^{38}$;
Forti, Alessandra$^{91}$;
Franzoni, Giovanni$^{5}$;
Frost, James$^{103}$;
Fuess, Stu$^{16,c}$;

@@

Gardner, Robert$^{79}$;
Garonne, Vincent$^{101}$;

@@

George, Simon$^{61}$;
Geurts, Frank$^{106}$;

@@

Giagu, Stefano$^{108,33}$;
Giffels, Manuel$^{41}$;
Gingrich, Douglas$^{69}$;

@@

Gligorov, Vladimir V.$^{50,b}$;
Glushkov, Ivan$^{113}$;
Gohn, Wesley$^{87}$;

@@

González Caballero, Isidro$^{102}$;
González Fernández, Juan R.$^{102}$;

@@

Grasland, Hadrien$^{44}$;
Gray, Heather$^{45}$;
Grillo, Lucia$^{91}$;
Guan, Wen$^{118}$;

@@

Gyurjyan, Vardan$^{39}$;
Hanushevsky, Andrew$^{62,p}$;

@@

Hauth, Thomas$^{41}$;

@@

Heinrich, Lukas$^{56}$;
Heiss, Andreas$^{41}$;

@@

Hildreth, Michael$^{98,f}$;
Hodgkinson, Mark$^{111}$;
Hoeche, Stefan$^{62,p}$;
Holzman, Burt$^{16,c}$;

@@

Huang, Xingtao$^{110}$;
Ivanchenko, Vladimir N.$^{5,114}$;
Ivanov, Todor$^{112}$;
Iven, Jan$^{5}$;
Jashal, Brij$^{67}$;

@@

Jones, Roger$^{88,a}$;
Jouvin, Michel$^{44,a}$;

@@

Kagan, Michael$^{62,p}$;
Kalderon, Charles William$^{90}$;
Kane, Meghan$^{64}$;

@@

Katz, Daniel S.$^{78}$;

@@

Keeble, Oliver$^{5}$;
Kersevan, Borut Paul$^{89}$;

@@

Klute, Markus$^{93}$;

@@

Konstantinov, Dmitri$^{59}$;
Koppenburg, Patrick$^{55}$;

@@

Kreczko, Luke$^{71}$;
Kuhr, Thomas$^{48,a}$;

@@

Lampl, Walter$^{70}$;

@@

Lange, David$^{105,a}$;

@@

Leggett, Charles$^{45}$;
Letts, James$^{74}$;

@@

Li, Teng$^{82}$;
Lima, Guilherme$^{16,c}$;
Linacre, Jacob$^{60,m}$;

@@

Livny, Miron$^{6}$;

@@

Love, Peter$^{88}$;
Lyon, Adam$^{16,c}$;

@@

Marshall, Zachary L$^{45}$;

@@

Martin-Haugh, Stewart$^{60}$;

@@

Mazumdar, Kajari$^{67}$;
McCauley, Thomas$^{98}$;

@@

McKee, Shawn$^{94,l}$;
McNab, Andrew$^{91}$;
Mehdiyev, Rashid$^{77}$;

@@

Mete, Alaettin Serhan$^{73}$;

@@

Mitrevski, Jovan$^{48}$;

@@

Morgan, Ben$^{117}$;
Mount, Richard$^{62,p}$;
Moyse, Edward$^{93}$;
Murray, Sean$^{76,10}$;
Nairz, Armin$^{5}$;
Neubauer, Mark S$^{78,a,k}$;
Norman, Andrew$^{16,c}$;
Novaes, Sérgio$^{107}$;

@@

Ozturk, Nurcan$^{113}$;
Pacheco Pages, Andres$^{58,20,j}$;
Paganini, Michela$^{119}$;
Pansanel, Jerome$^{36}$;
Pascuzzi, Vincent R.$^{115}$;
Patrick, Glenn$^{60}$;

@@

Pearson, Ben$^{53}$;

@@

Perdue, Gabriel$^{16,c}$;
Perez-Calero Yzquierdo, Antonio$^{58,7,g}$;

@@

Petersen, Troels$^{54}$;

@@

Petzold, Andreas$^{41}$;

@@

Piilonen, Leo$^{122,i}$;

@@

Pivarski, Jim$^{105}$;

@@

Polci, Francesco$^{50}$;

@@

Puig Navarro, Albert$^{120}$;
Quast, Günter$^{41}$;
Raven, Gerhard$^{55,123}$;

@@

Ritter, Martin$^{48}$;

@@

Rodrigues, Eduardo$^{80,a,e}$;

@@

Rousseau, David$^{44}$;
Roy, Gareth$^{85}$;
Rybkine, Grigori$^{44}$;

@@

Sakuma, Tai$^{71}$;

@@

Sartirana, Andrea$^{47}$;
Schellman, Heidi$^{57}$;

@@

Schramm, Steven$^{84}$;

@@

Seidel, Sally$^{97}$;
Sekmen, Sezen$^{43}$;
Serfon, Cedric$^{101}$;
Severini, Horst$^{99}$;

@@

Seymour, Michael$^{91}$;
Sgalaberna, Davide$^{5}$;
Shapoval, Illya$^{45}$;

@@

Shiu, Jing-Ge$^{66}$;

@@

Skipsey, Sam$^{85}$;

@@

Sokoloff, Michael D$^{80,a}$;
Spentzouris, Panagiotis$^{16,c}$;

@@

Stark, Giordon$^{79}$;
Stewart, Gordon$^{85}$;

@@

Sánchez, Arturo$^{116,19}$;

@@

Taffard, Anyes$^{73}$;
Tamponi, Umberto$^{35}$;
Templon, Jeff$^{55}$;

@@

Tsulaia, Vakhtang$^{45}$;
Tunnell, Christopher$^{79}$;

@@

Vallecorsa, Sofia$^{83}$;

@@

Votava, Margaret$^{16,c}$;
Vuosalo, Carl$^{118}$;
Vázquez Sierra, Carlos$^{55}$;

@@

Watts, Gordon T$^{109}$;

@@

Williams, Mike$^{52}$;
Winklmeier, Frank$^{57}$;

@@

Wuerthwein, Frank$^{74}$;
Wynne, Benjamin$^{82}$;

@@

Yang, Wei$^{62,p}$;

@@

\par {\footnotesize $^{6}$ Center for High Throughput  Computing, Computer Sciences Department, University of Wisconsin-Madison, Madison, WI, USA}

@@

\par {\footnotesize $^{11}$ California Institute of Technology, Pasadena, California, CA, USA}
\par {\footnotesize $^{12}$ Cornell University, Ithaca, NY, USA}

@@

\par {\footnotesize $^{15}$ ETH Zürich - Institute for Particle Physics and Astrophysics (IPA), Zürich, Switzerland}
\par {\footnotesize $^{16}$ Fermi National Accelerator Laboratory, Batavia, IL, USA}

@@

\par {\footnotesize $^{24}$ Department of Physics, Indiana University, Bloomington, IN, USA}

@@

\par {\footnotesize $^{35}$ INFN Sezione di Torino, Torino, Italy}
\par {\footnotesize $^{36}$ Université de Strasbourg, CNRS, IPHC UMR 7178, F-67000 Strasbourg, France}
\par {\footnotesize $^{37}$ Imperial College London, London, United Kingdom}
\par {\footnotesize $^{38}$ DSM/IRFU (Institut de Recherches sur les Lois Fondamentales de l’Univers), CEA Saclay (Commissariat à l’Énergie Atomique), Gif-sur-Yvette, France}
\par {\footnotesize $^{39}$ Thomas Jefferson National Accelerator Facility, Newport News, Virginia, VA, USA}
\par {\footnotesize $^{40}$ Jožef Stefan Institute, Ljubljana, Slovenia}
\par {\footnotesize $^{41}$ Karlsruhe Institute of Technology, Karlsruhe, Germany}
\par {\footnotesize $^{42}$ AGH University of Science and Technology, Faculty of Physics and Applied Computer Science, Krakow, Poland}
\par {\footnotesize $^{43}$ Kyungpook National University, Daegu, Republic of Korea}
\par {\footnotesize $^{44}$ LAL, Université Paris-Sud and CNRS/IN2P3, Orsay, France}
\par {\footnotesize $^{45}$ Lawrence Berkeley National Laboratory and University of California, Berkeley, CA, USA}
\par {\footnotesize $^{46}$ Laboratório de Instrumentação e Física Experimental de Partículas (LIP), Lisboa, Portugal}
\par {\footnotesize $^{47}$ Laboratoire Leprince-Ringuet, École Polytechnique, CNRS/IN2P3, Université Paris-Saclay, Palaiseau, France}
\par {\footnotesize $^{48}$ Fakultät für Physik, Ludwig-Maximilians-Universität München, München, Germany}
\par {\footnotesize $^{49}$ Laboratoire de Physique Corpusculaire, Clermont Université and Université Blaise Pascal and CNRS/IN2P3, Clermont-Ferrand, France}
\par {\footnotesize $^{50}$ Laboratoire de Physique Nucléaire et de Hautes Energies (LPNHE), Sorbonne Université, Université Paris Diderot, CNRS/IN2P3, Paris, France}
\par {\footnotesize $^{51}$ Laboratoire de Physique Subatomique et de Cosmologie, Université Joseph Fourier and CNRS/IN2P3 and Institut National Polytechnique de Grenoble, Grenoble, France}
\par {\footnotesize $^{52}$ Massachusetts Institute of Technology, Cambridge, MA, USA}
\par {\footnotesize $^{53}$ Max-Planck-Institut für Physik (Werner-Heisenberg-Institut), München, Germany}
\par {\footnotesize $^{54}$ Niels Bohr Institute, University of Copenhagen, Kobenhavn, Denmark}
\par {\footnotesize $^{55}$ Nikhef National Institute for Subatomic Physics, Amsterdam, Netherlands}
\par {\footnotesize $^{56}$ Department of Physics, New York University, New York, NY, USA}
\par {\footnotesize $^{57}$ Center for High Energy Physics, University of Oregon, Eugene, OR, USA}
\par {\footnotesize $^{58}$ Port d’Informació Científica (PIC), Universitat Autònoma de Barcelona (UAB), Barcelona, Spain}
\par {\footnotesize $^{59}$ High Energy Physics (IHEP), Protvino, Russia}
\par {\footnotesize $^{60}$ STFC Rutherford Appleton Laboratory, Didcot, United Kingdom}
\par {\footnotesize $^{61}$ Department of Physics, Royal Holloway University of London, Surrey, United Kingdom}
\par {\footnotesize $^{62}$ SLAC National Accelerator Laboratory, Menlo Park, CA, USA}
\par {\footnotesize $^{63}$ Simons Foundation, New York, NY, USA}
\par {\footnotesize $^{64}$ SoundCloud, Berlin, Germany}
\par {\footnotesize $^{65}$ SUBATECH, IMT Atlantique, Université de Nantes, CNRS-IN2P3, Nantes, France}
\par {\footnotesize $^{66}$ National Taiwan University, Taipei, Taiwan}
\par {\footnotesize $^{67}$ Tata Institute of Fundamental Research, Mumbai, India}
\par {\footnotesize $^{68}$ Technische Universit\"at Dortmund, Dortmund, Germany}
\par {\footnotesize $^{69}$ Department of Physics, University of Alberta, Edmonton, AB, Canada}
\par {\footnotesize $^{70}$ Department of Physics, University of Arizona, Tucson, AZ, USA}
\par {\footnotesize $^{71}$ H.H. Wills Physics Laboratory, University of Bristol, Bristol, United Kingdom}
\par {\footnotesize $^{72}$ Department of Physics, University of British Columbia, Vancouver, BC, Canada}
\par {\footnotesize $^{73}$ Department of Physics and Astronomy, University of California Irvine, Irvine, CA, USA}
\par {\footnotesize $^{74}$ University of California, San Diego, La Jolla, CA, USA}
\par {\footnotesize $^{75}$ Cavendish Laboratory, University of Cambridge, Cambridge, United Kingdom}
\par {\footnotesize $^{76}$ Physics Department, University of Cape Town, Cape Town, South Africa}
\par {\footnotesize $^{77}$ Carleton University, Ottawa, ON, Canada}
\par {\footnotesize $^{78}$ University of Illinois Urbana-Champaign, Champaign, Illinois, IL, USA}
\par {\footnotesize $^{79}$ Enrico Fermi Institute, University of Chicago, Chicago, IL, USA}
\par {\footnotesize $^{80}$ University of Cincinnati, Cincinnati, OH, USA}
\par {\footnotesize $^{81}$ Department of Physics, Duke University, Durham, NC, USA}
\par {\footnotesize $^{82}$ SUPA - School of Physics and Astronomy, University of Edinburgh, Edinburgh, United Kingdom}
\par {\footnotesize $^{83}$ Gangneung-Wonju National University, South Korea}
\par {\footnotesize $^{84}$ Section de Physique, Université de Genève, Geneva, Switzerland}
\par {\footnotesize $^{85}$ SUPA - School of Physics and Astronomy, University of Glasgow, Glasgow, United Kingdom}
\par {\footnotesize $^{86}$ Physikalisches Institut, Ruprecht-Karls-Universitat Heidelberg, Heidelberg, Germany}
\par {\footnotesize $^{87}$ Department of Physics and Astronomy, University of Kentucky, Lexington, KY, USA}
\par {\footnotesize $^{88}$ Physics Department, Lancaster University, Lancaster, United Kingdom}
\par {\footnotesize $^{89}$ Department of Physics, Jožef Stefan Institute and University of Ljubljana, Ljubljana, Slovenia}
\par {\footnotesize $^{90}$ Fysiska institutionen, Lunds Universitet, Lund, Sweden}
\par {\footnotesize $^{91}$ School of Physics and Astronomy, University of Manchester, Manchester, United Kingdom}
\par {\footnotesize $^{92}$ University of Maribor, Ljubljana, Slovenia}
\par {\footnotesize $^{93}$ Department of Physics, University of Massachusetts, Amherst, MA, USA}
\par {\footnotesize $^{94}$ Department of Physics, The University of Michigan, Ann Arbor, MI, USA}
\par {\footnotesize $^{95}$ Departamento de Física, Universidade do Minho, Braga, Portugal}
\par {\footnotesize $^{96}$ University of Nebraska-Lincoln, Lincoln, NE, USA}
\par {\footnotesize $^{97}$ Department of Physics and Astronomy, University of New Mexico, Albuquerque, NM, USA}
\par {\footnotesize $^{98}$ University of Notre Dame, Notre Dame, IN, USA}
\par {\footnotesize $^{99}$ Homer L. Dodge Department of Physics and Astronomy, University of Oklahoma, Norman, OK, USA}
\par {\footnotesize $^{100}$ The Ohio State University, Columbus, OH, USA}
\par {\footnotesize $^{101}$ Department of Physics, University of Oslo, Oslo, Norway}
\par {\footnotesize $^{102}$ Universidad de Oviedo, Oviedo, Spain}
\par {\footnotesize $^{103}$ Department of Physics, Oxford University, Oxford, UK}
\par {\footnotesize $^{104}$ Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, PA, USA}
\par {\footnotesize $^{105}$ Princeton University, Princeton, NJ, USA}
\par {\footnotesize $^{106}$ Rice University, Houston, TX, USA}
\par {\footnotesize $^{107}$ Universidade Estadual Paulista, São Paulo, Brazil}
\par {\footnotesize $^{108}$ Dipartimento di Fisica, Università La Sapienza, Roma, Italy}
\par {\footnotesize $^{109}$ University of Washington, Seattle, WA, USA}
\par {\footnotesize $^{110}$ School of Physics, Shandong University, Shandong, China}
\par {\footnotesize $^{111}$ Department of Physics and Astronomy, University of Sheffield, Sheffield, United Kingdom}
\par {\footnotesize $^{112}$ University of Sofia, Sofia, Bulgaria}
\par {\footnotesize $^{113}$ Department of Physics, The University of Texas at Arlington, Arlington, TX, USA}
\par {\footnotesize $^{114}$ National Research Tomsk Polytechnic University, Tomsk, Russia}
\par {\footnotesize $^{115}$ Department of Physics, University of Toronto, Toronto, ON, Canada}
\par {\footnotesize $^{116}$ Dipartimento di Chimica, Fisica e Ambiente, Università di Udine, Udine, Italy}
\par {\footnotesize $^{117}$ Department of Physics, University of Warwick, Coventry, United Kingdom}
\par {\footnotesize $^{118}$ University of Wisconsin - Madison, Madison, WI, USA}
\par {\footnotesize $^{119}$ Department of Physics, Yale University, New Haven, CT, USA}
\par {\footnotesize $^{120}$ Physik-Institut, Universität Zürich, Zürich, Switzerland}
\par {\footnotesize $^{121}$ IOP and GUST, Vietnam Academy of Science and Technology (VAST), Hanoi, Vietnam}
\par {\footnotesize $^{122}$ Virginia Tech, Blacksburg, Virginia, VA, USA}
\par {\footnotesize $^{123}$ Vrije Universiteit Amsterdam, Amsterdam, The Netherlands}
